---
title: "Final Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("./plot_functions.R")
source("./inference_functions.R")
```

## Ian Evans

This package is intended to improve understanding and analysis of COVID-19 data. The following dataset is used for analysis. <https://cran.r-project.org/web/packages/COVID19/index.html>  
Goals:
  1) Import Covid19 data into R and create an assortment of data visualizations.
  2) Infer infection rates related to COVID by calculating the difference between predicted death rates for 2020 and deaths we have seen so far with COVID.
  3) Determine if there's any correlation between this difference, which should correspond to the positivity rate if both are accurate measures.

## 1

The following basic plots were included in this package. The functionality of these plots could be expanded upon to include: focusing on specific dates, different comparisons of variables, or user defined expressions using quosures.

```{r, echo=TRUE, message = FALSE, warning=FALSE}
plot_deaths()
plot_tests()
plot_positiveTests()
plot_positivityOfTest()
plot_countyDeaths() #Note this function does not currently work as intended
```


## 2
#Indiana Death Statistics obtained from: http://www.stats.indiana.edu/vitals/
```{r, echo=TRUE, message = FALSE, warning=FALSE}
plot_death_difference()
```



